API design for machine learning software: experiences from the scikit-learn project

### 2013-09-27 paper.tex
numerical citations to save space

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
%\usepackage{hyperref}
\usepackage{minted}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}

@@

Our rule of thumb is that user code should not be tied to \sklearn---which is a
\textit{library}, not a framework. We try to avoid a
common problem with object-oriented design: that users wanting a
``banana'' instead get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited by \citealp[p.~213]{seibel2009coders}).
Programs using \sklearn should not be intimately tied to it,
so that their code can be reused or in other contexts.

@@

While part of the \sklearn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.
The power and extensibility of the \sklearn API is evidenced
by the large and growing user-base, its use to solve real
problems across a wide array of fields,
as well as the appearance of third-party packages
that follow \sklearn conventions. Examples of such packages include
\textit{astroML}\footnote{\url{http://astroml.org}}
\citep{vanderplas2012astroML}, a machine learning toolkit for astronomy,
and \textit{wiseRF}\footnote{\url{http://wise.io}}, a commercial random forest
implementation. The source code of the recently-proposed sparse multiclass
algorithm of \citet{mblondel-mlj2013}, released as part of the
\textit{lightning}\footnote{\url{https://github.com/mblondel/lightning}}
package, also follows the \sklearn conventions.
We encourage researchers to follow these conventions when releasing software.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
%\usepackage{hyperref}
\usepackage{minted}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}

@@

Our rule of thumb is that user code should not be tied to \sklearn---which is a
\textit{library}, not a framework. We try to avoid a
common problem with object-oriented design: that users wanting a
``banana'' instead get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited in \citep[p.~213]{seibel2009coders}).
Programs using \sklearn should not be intimately tied to it,
so that their code can be reused or in other contexts.

@@

While part of the \sklearn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.
The power and extensibility of the \sklearn API is evidenced
by the large and growing user-base, its use to solve real
problems across a wide array of fields,
as well as the appearance of third-party packages
that follow \sklearn conventions. Examples of such packages include
\textit{astroML}\footnote{\url{http://astroml.org}}
\citep{vanderplas2012astroML}, a machine learning toolkit for astronomy;
\textit{wiseRF}\footnote{\url{http://wise.io}}, a commercial random forest implementation;
and \textit{lightning},\footnote{\url{https://github.com/mblondel/lightning}}
the source code of a recently-proposed sparse multiclass
algorithm \citep{mblondel-mlj2013}.
We encourage researchers to follow these conventions when releasing software.
